---
documentclass: jss
author:
  - name: Gilberto Camara
    orcid: 0000-0002-3681-487X
    affiliation: National Inst for Space Research, \\ Brazil
    # use this syntax to add text on several lines
    address: |
      | Avenida dos Astronautas, 1758
      | 12227-001 Sao Jose dos Campos, Brazil
    email: \email{gilberto.camara```inpe.br}
  - name: Rolf Simoes
    orcid: 0000-0003-0953-4132
    affiliation: National Inst for Space Research, Brazil
    # To add another line, use \AND at the end of the previous one as above
  - name: Renato Assunção
    orcid: 0000-0001-7442-9166
    affiliation: Federal Univ of Minas Gerais, Brazil \AND
  - name: Alexandre Carvalho
    orcid: 0000-0001-8762-5465
    affiliation: Inst for Applied Economic Research, Brazil
  - name: Felipe Souza
    orcid: 0000-XXXXX
    affiliation: National Inst for Space Research, Brazil
  - name: Pedro Ribeiro de Andrade
    orcid: 0000-XXXXX
    affiliation: National Institute for Space Research, Brazil        
title:
  formatted: "Bayesian inference for smoothing of remote sensing image classification using machine learning"
  # If you use tex in the formatted title, also supply version without
  plain:     "Bayesian smoothing for image classification"
  # For running headers, if needed
  short:     "Bayesian smoothing for image classification"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [Bayesian smoothing, image classification, machine learning, "\\proglang{R}"]
  plain:     [Bayesian smoothing, image classification, machine learning, R]
preamble: >
  \usepackage{amsmath}
  \usepackage[english]{babel}
  \usepackage{microtype}
  \usepackage{graphicx}
  \usepackage{booktabs}
  \usepackage{float}
  \usepackage{flafter}
  \usepackage{placeins}
  \usepackage[all,defaultlines=3]{nowidow}
  \usepackage[T1]{fontenc}
  \usepackage[adobe-utopia]{mathdesign}
  \renewcommand*\ttdefault{txtt}
bibliography: e-sensing.bib
biblio-style: apalike
csl: ieee.csl
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
---

```{r, setup, include=FALSE, echo = FALSE}
options(prompt = 'R> ', continue = '+ ')
# if sits is not installed, install it
if (!requireNamespace("sits", quietly = TRUE))
    install.packages("sits", repos = "https://cloud.r-project.org/")
library("sits")
# if sitsdata is not installed, get it
if (!requireNamespace("sitsdata", quietly = TRUE))
    devtools::install_github("e-sensing/sitsdata")
library(sitsdata)
sits:::.conf_set_options("tmap_legend_text_size" = 0.7)
sits:::.conf_set_options("tmap_legend_title_size" = 0.7)
sits:::.conf_set_options("tmap_max_cells" = 1e+09)
knitr::opts_chunk$set(echo = TRUE, fig.pos = "h")
```
\newpage
# Introduction

Image classification post-processing has been defined as \textit{"a refinement of the
labelling in a classified image in order to enhance its classification accuracy"}
\citep{Huang2014}. In remote sensing image analysis, these procedures are used
to combine pixel-based classification methods with a spatial post-processing
method to remove outliers and misclassified pixels. For pixel-based classifiers,
post-processing methods enable the inclusion of spatial information
in the final results.

Smoothing methods are an important complement to machine learning algorithms
for image classification. Methods such as support vector machines
\citep{Mountrakis2011}, random forests \citep{Belgiu2016} and
deep learning \citep{Ma2019} are becoming increasingly popular. Since these methods 
are mostly pixel-based,it is useful to complement them with post-processing smoothing 
to include spatial information in the result.

A traditional choice for smoothing classified images is the majority filter, 
where the class of the central pixel is replaced by the most frequent class of 
the neighbourhood. This technique is rather simplistic; more sophisticated methods 
use class probabilities. For each pixel, machine learning and other statistical 
algorithms provide the probabilities of that pixel belonging to each of the classes. 
As a first step in obtaining a result, each pixel is assigned to the class whose 
probability is higher. After this step, smoothing methods use class probabilities 
to detect and correct outliers or misclassified pixels.

Probability-based smoothing methods include Gaussian and edge-aware filtering \citep{Schindler2012}, modal filters \citep{Ghimire2010} and probabilistic relaxation 
\citep{Gong1989}. \citet{Huang2014} propose a relearning method based on co-ocurrence 
matrices; these matrices represent the joint distribution of class labels in the 
neighborhood of each pixel. In the current work, we introduce a Bayesian smoothing method, 
which provides the means to incorporate prior knowledge in data analysis.

Bayesian inference can be thought of as way of coherently updating our uncertainty in the 
light of new evidence. It allows the inclusion of expert knowledge on the derivation of 
probabilities. As stated by \citet{Spiegelhalter2009}: "In the Bayesian paradigm, degrees 
of belief in states of nature are specified. Bayesian statistical methods start with 
existing 'prior' beliefs, and update these using data to give 'posterior' beliefs, 
which may be used as the basis for inferential decisions". 

Bayesian smoothing methods have become an established technique for image restoration and reconstruction \citep{Hanson1993}. More recently, \citet{Wu2017} proposed a Bayesian 
approach for soft fusion applied to change detection. However, to the best of our knowledge 
this work is the first proposal to use Bayesian smoothing for post-processing of machine 
learning pixel based classification.

% TODO: include a paragraph about R packages following the style below
In \proglang{R}, ...include here a discussion of what's available in R, and 
include mention to the \pkg{sits} package

The \pkg{sits} package uses satellite image time series for land classification, using  
a time-first, space-later approach \cite{Simoes2021}. In the data preparation part, 
collections of big Earth observation images are organized as data cubes. 
Each spatial location of a data cube 
is associated with a time series. Locations with known labels train a machine learning 
classifier, which classifies all time series of a data cube. The package has tools for 
analysis, visualization, and classification of satellite image time series.

# Methods

## Conversion from probabilities to logits

The proposed post-classification smoothing model considers the output of a machine 
learning algorithm that provides the probabilities of each pixel in the image to belong 
to target classes. More formally, let $p_{i,k}$ be the probability of pixel 
$i$ belonging to class $k$, $k=1,\dots{},K$, then

\begin{equation}
\sum_{k=1}^K p_{i,k} = 1, p_{i,k} > 0.
\end{equation}

To more the inference tractable, the class probability values $p_{i,k}$ are converted to 
log-odds values. The logit function converts probability values from 
0 to 1 to values from $-\infty$ to $\infty$. The conversion from probabilities to logit 
values is useful to support the assumption of normal distribution for the data. 
The conversion is expressed by

\begin{equation}
x_{i,k} = \ln \left(\frac{p_{i,k}}{1 - p_{i,k}}\right)
\end{equation}

Confidence in pixel classification increases with logit. There are situations, such as 
border pixels or mixed ones, where the logit of different classes are similar in magnitude. 
These are cases of low confidence in the classification result. To assess and correct these 
cases, the post-classification smoothing method borrows strength from the neighbors and 
reduces the variance of the estimated class.

## Bayesian inference

After the transformation of probability values into logits, the problem can be expressed 
in a Bayesian context. Suppose that $x\in{}X$ has a distribution 
$\pi(x|\theta)$ with an unknown $\theta{}\in{}\Theta{}$ parameter. Consider two random 
variables for each pixel $i$ and class$k$: (a) $x_{i,k}$, the observed class logits; 
(b) $\mu_{i,k}$, the inferred logit values based on the observations. From the output of 
the machine learning classification is $x_{i,k}$, the aim is to estimate the actual 
values $\mu_{i,k} | x_{i,k}$. The Bayesian inference procedure can be expressed as

\begin{equation}
\pi(\mu|x) \propto{} \pi(x|\mu)\pi(\mu).
\end{equation}

To estimate the conditional posterior distribution $\pi(\mu|x)$, we combine two 
distributions: (a) the distribution $\pi(x|\mu)$, known as the likelihood, 
which expresses how measured values $x_{i,k}$ depend in the underlying values $\mu_{i,k}$; 
and (b) $\pi(\mu)$, which is our guess on the actual data distribution, known as the prior. 
For simplicity, independence between the different classes $k$ is assumed. Therefore, the 
update will be performed for each class $k$ separately.

The method assumes that the likelihood $x_{i,k} | \mu_{i,k}$ follows a normal 
distribution $N(\mu_{i,k}, \sigma^2_{k})$ with parameters $\mu_{i,k}$ and $\sigma^2_{k}$. 
The variance $\sigma^2_{k}$ will be estimated based on user expertise and taken as 
a hyperparameter to control the smoothness of the resulting estimate. Therefore

\begin{equation}
x_{i,k} | \mu_{i,k} \sim N(\mu_{i,k}, \sigma^2_{k})
\end{equation}

is the likelihood. We will also assume a normal local prior for the 
parameter $\mu_{i,k}$ with parameters $m_{i,k}$ and $s^2_{i,k}$:

\begin{equation}
	\mu_{i,k} \sim N(m_{i,k}, s^2_{i,k}).
\end{equation}

To calculate the prior, the method assumes that the class probabilities in the spatial
neighbourhood of the pixel have the same distribution. Estimating the local means and variances 
for the prior distribution considers a spatial neighbourhood $N_{i}$ close to pixel $p_i$. 
Let $\#(N_{i})$ be the number of elements in the neighbourhood $N_{i}$. 
The mean value is given by

\begin{equation}
m_{i,k} = \frac{\sum_{(j) \in N_{i}} x_{j,k}}{\#(N_{i})}
\end{equation}

and the variance by

\begin{equation}
s^2_{i,k} = \frac{\sum_{(j) \in N_{i}} [x_{j,k} - m_{i,k}]^2}{\#(N_{i})-1}.
\end{equation}

Given these assumptions, the Bayesian update for the expected conditional mean 
${E}[\mu_{i,k} | x_{i,k}]$ is given by:

\begin{equation}
{E}[\mu_{i,k} | x_{i,k}] = \frac{m_{i,t} \times \sigma^2_{k} +
x_{i,k} \times s^2_{i,k}}{ \sigma^2_{k} +s^2_{i,k}}
\end{equation}

which can be expressed as a weighted mean

\begin{equation}
{E}[\mu_{i,k} | x_{i,k}] =
\Biggl [ \frac{s^2_{i,k}}{\sigma^2_{k} +s^2_{i,k}} \Biggr ] \times
x_{i,k} +
\Biggl [ \frac{\sigma^2_{k}}{\sigma^2_{k} +s^2_{i,k}} \Biggr ] \times m_{i,k}
\end{equation}

where

\begin{itemize}
\item $x_{i,k}$ is the logit value for pixel $i$ and class $k$.
\item $m_{i,k}$ is the average of logit values for pixels of class $k$ 
in the neighborhood of pixel $i$.
\item $s^2_{i,k}$ is the variance of logit values for pixels of class $k$ 
in the neighborhood of pixel $i$.
\item $\sigma^2_{k}$ is the prior variance of the logit values for class $k$, 
and is an user-derived hyperparameter.
\end{itemize}

The above equation is a weighted average between the value $x_{i,k}$ for the pixel 
and the mean $m_{i,k}$ for the neighboring pixels. When the variance $s^2_{i,k}$ for the 
neighbors is too high, the algorithm gives more weight to the pixel value $x_{i,k}$. 
On the other hand, when the noise $\sigma^2_k$ increases, the method gives more weight 
to the neighborhood mean $m_{i,k}$.

\newpage

## Effect of the hyperparameter

The parameter $\sigma^2_k$ controls the level of smoothness. If $\sigma^2_k$ is zero, 
the smoothed value ${E}[\mu_{i,k} | x_{i,k}]$ will be equal to the pixel value $x_{i,k}$. 
Making $\sigma^2_k$ high leads to much smoothness. Values of the prior variance 
$\sigma^2_{k}$, which are small relative to the local variance $s^2_{i,k}$ increase our 
confidence in the original probabilities. Conversely, prior variances $\sigma^2_{k}$ 
which are large relative to the local variance $s^2_{i,k}$ increase our confidence in 
the average probability of the neighborhood.

Thus, the parameter $\sigma^2_{k}$ expresses our confidence in the inherent variability 
of the distribution of values of a class $k$. The smaller the parameter $\sigma^2_{k}$, 
the more we trust the estimated probability values produced by the classifier for class $k$. 
Conversely, higher values of $\sigma^2_{k}$ indicate lower confidence in the classifier 
outputs and improved confidence in the local average values.

Consider the following two-class example. Take a pixel with probability 0.4 
(logit $x_{i,1}$ = -0.4054) for class A, and probability 0.6 (logit $x_{i,2}$ = 0.4054) 
for class B. Without post-processing, the pixel will be labeled as class B. Consider that 
the local average is 0.6 (logit $m_{i,1}$ = 0.4054) for class A and 0.4 
(logit $m_{i,2}$ = -0.4054) for class B. This is a case of an outlier classified 
originally as class B in the midst of a set of pixels of class A. Take the local variance 
of logits to be $s^2_{i,1}$ = 5 for class A and $s^2_{i,2}$ = 10 and for class B. 
This difference is to be expected if the local variability of class A is smaller 
than that of class B.

To complete the estimate, we need to set the parameter $\sigma^2_{k}$, representing prior 
belief in the variability of the probability values for each class. If we take both 
$\sigma^2_{A}$ for class A and $\sigma^2_{B}$ for class B to be both 10, the Bayesian 
estimated probability for class A is 0.52  and for class B is 0.48. In this case, the pixel 
will be relabeled as being class A. However, if our belief in the original values is higher, 
we will get a different result. If we set $\sigma^2$ to be 5 for both classes A and B, 
the Bayesian probability estimate will be 0.48 for class A and 0.52 for class B. 
In this case, the original label will be kept.

## Defining the neighbourhood

The intuition for Bayesian smoothing is that homogeneous neighbourhoods should have a 
dominant class that has both higher average probabilities and lower variance than the others. 
In these neighbourhoods, a pixel of a different class is likely to be associated 
to lower average probabilities and higher local variance. Thus, the post-processing
will not change the most likely class for pixels in spatially homogenous regions.

The rationale behind Bayesian smoothing is that areas with similar characteristics have a dominant class that has higher average probabilities and lower variance than other classes. 
In such regions, a pixel with a different class is expected to have lower average 
probabilities and higher local variance. Post-processing should not change the most likely 
class for pixels in these regions.

When pixels are located at the borders between areas with different classes, they contain 
signatures of two classes, which poses a classification problem. For local class statistics to be reliable, only pixels likely to belong to this class should be included. When windows are 
centered on border pixels, only some of the pixels in the window belong to the same class as the central pixel; the others belong to a different class. To account for border pixels, 
sits uses a special definition of a neighbourhood to estimate the prior class distribution. 

To estimate prior distribution using spatial neighbourhood, the algorithm only uses
pixels with high probability of belonging to the class. The logic is that pixels with 
low probabilities are unlikely to belong to the same class distribution as those with 
high probability values. This procedure ensures a more reliable estimate of the prior.

# Software and examples

## Reading a probability data cube
 
The input for the \pkg{sits} post-classification is an image file with the probabilities produced by a machine learning algorithm. This file should be multi-band, where each band contains the pixel probabilities of a single class. The image should be GDAL-readable with INT2S data type with values ranging  from [0..10000]. The file name should have  information on reference dates and includes a version number. The following code creates a probability cube from a file produced by a random forests classification applied to a data cube of Sentinel-2 images, covering tile "20LLQ" in the Brazilian Amazonia covering the period from 2020-06-04 to 2021-08-26. The original analysis-ready files were obtained from Microsoft Planetary Computer. The training data has six classes: (a) \code{Forest} for natural tropical forest; (b) \code{Water} for lakes and rivers; (c) \code{Wetlands} for areas where water covers the soil in the wet season; (d) \code{ClearCut_Burn} for areas where fires cleared the land after tree removal. (e) \code{ClearCut_Soil} where the forest has been removed; (f) \code{ClearCut_Veg} where some vegetation remains after most trees have been removed.

The first step is informing the location of the file. In this case, the image containing
the probabilities is provided by the \pkg{sitsdata} package.

```{r, echo = TRUE, eval = TRUE}
data_dir <- system.file("/extdata/Rondonia-20LLQ/", package = "sitsdata")
list.files(data_dir)
```

The class labels should also be informed by the user, since they are not stored in image files. 
```{r, echo = TRUE, eval = TRUE}
labels <- c("Water", "ClearCut_Burn", "ClearCut_Soil",
            "ClearCut_Veg", "Forest", "Wetland")
```

In \pkg{sits}, \code{sits_cube()} builds an object describing the image; its main parameters are: (a) \code{source}: data provider. Examples are "AWS" and "MPC"; (b)\code{collection}: image collection on the data provider, e.g., "SENTINEL-2-L2A" (Sentinel-2 collection from MPC); (c)\code{data_dir}: directory where the image is available; (d)\code{bands}: Band names associated with the data, in this case \code{probs};  (e) \code{labels}: Labels with the training classes; (f) \code{version}: version of the result; (g) \code{parse_info}: how to extract `tile`, `band`, `date` and `version` information from the file name. It includes designators such as `X1` and `X2` which are place holders for parts of the file name that is not relevant.

```{r, tidy="styler", echo=TRUE, eval=TRUE}
probs_cube <- sits_cube( 
  source = "MPC",
  collection = "SENTINEL-2-L2A",
  bands = "probs",
  labels = labels,
  parse_info = c(
    "X1", "X2", "tile", "start_date", "end_date", "band", "version"),
  data_dir = data_dir)
```

The output of \code{sits_cube()} is a tibble that contains metadata about the probability maps and associated file. Figure \@ref(fig:pcube) shows the layers of the data cube. The map for class \code{Forest} shows high probability values associated with compact patches and linear stretches in riparian areas. Class \code{ClearCut_Soil} is mostly composed of dense areas of high probability whose geometrical boundaries result from forest cuts. By contrast, the probability maps for classes \code{Water}, \code{ClearCut_Burn} and \code{ClearCut_Veg} have mostly low values. 

```{r pcube, width = 9, tidy="styler", fig.align = 'center', fig.cap = "Class probabilities produced by random forest algorithm."}
plot(probs_cube)
```


To show the need for post-processing, it is useful to produce a non-smoothed labelled map. The map is obtained by taking the class of higher probability for each pixel as its label without considering the spatial context. This is done by \code{sits_label_classification()} whose main parameters are: (a) \code{cube}, a probability cube; (b) \code{output_dir}, directory for storing results; (c) \code{version}. 
```{r, echo=TRUE, eval=TRUE}
label_cube_no_smooth <- sits_label_classification(
    cube = probs_cube,
    output_dir = tempdir(),
    version = "no_smooth")
```
Figure \@ref(fig:map1) shows the resulting map, which contains a significant number of outliers and pixels likely to be misclassified.

```{r map1, width = 7, tidy="styler", fig.align = 'center', fig.cap = "Labelled map without smoothing."}
plot(label_cube_no_smooth)
```

## Estimating the local logit variances

Before applying the Bayesian smoothing procedure to remove outliers, it is useful to consider the spatial distribution and the histogram of the logit variances, which correspond to the $s^2_{i,k}$ parameter in the Bayesian estimator. For this purpose, \code{sits_variance()} estimates the local logit variances. Its main parameters are: (a) \code{cube}, a probability cube; (b) \code{window_size}, the dimension of the local neighbourhood; (c) \code{neigh_fraction}, the percentage of pixels in the neighbourhood used to calculate the variance; (d) \code{output_dir}, directory where results will be stored. The example uses half of the pixels of a 7x7 window to estimate the variance. The chosen pixels will be those with the highest probability pixels to be more representative of the actual class distribution. The output values are the logit variances in the vicinity of each pixel. 

```{r, echo=TRUE, eval=TRUE}
var_cube <- sits_variance(
    cube = probs_cube,
    window_size = 7,
    neigh_fraction = 0.5,
    output_dir = tempdir())
summary(var_cube, only_stats = TRUE)
```

The choice of the 7 x 7 window size is a compromise between having enough values to 
estimate the parameters of a normal distribution and the need to capture local effects 
for class patches of small sizes. Classes such as \code{Water} and \code{ClearCut_Burn}
tend to be spatially limited; a bigger window size could result in invalid values for
their respective normal distributions.

The summary statistics show that most local variance values are low, which is an expected result. Areas of low variance correspond to pixel neighbourhoods of high logit values for one the classes and low logit values for the others. High values of the local variances are relevant in areas of confusion between classes. Figure \@ref(fig:vcube) shows the values of local logit variances for classes \code{ClearCut_Veg} and class \code{Forest}, considering only the 4th quartile of the distribution. Only the top 25% of the values for each class are shown, emphasizing areas of high local variability. 

```{r vcube, width = 9, tidy="styler", fig.align = 'center', fig.cap = "Logit variance map showing values above the 3rd quartile."}
plot(var_cube, percentile = 0.75, labels = c("ClearCut_Veg", "Forest"))
```

Comparing the logit variance maps of Figure \@ref(fig:vcube) with the probability maps of Figure \@ref(fig:pcube) shows the relevance of expert knowledge. The areas of high probability of class \code{Forest} are mostly made of compact patches; areas of high local variance occur near the borders of these patches. By contrast, class \code{ClearCut_Veg} represents a transition between natural forest areas and places where all trees have been cut, which are associated to class \code{ClearCut_Soil}. Class \code{ClearCut_Veg} has a high spectral variability, since the extent of remaining vegetation after most trees have been removed is not uniform. For this reason, the local variance of class \code{ClearCut_Veg} is mostly patch-based, while that of class \code{Forest} is mostly border-based. 

Further insights into the local variance are provided by Figure \@ref(fig:vhist) which shows the histograms of local variances per class. The values shown correspond to the 4th quartile (greater that 75% of all values) . The distribution of logit variances is uneven between the classes. Class \code{ClearCut_Veg} has a more balanced distribution, while most values in the 4th quartile of the \code{ClearCut_Soil} class have low values. 

```{r vhist, width = 9, tidy="styler", fig.align = 'center', fig.cap = "Histogram of logits of class variances above the 3rd quartile."}
plot(var_cube, type = "hist")
```

## Applying Bayesian smoothing to remove outliers

To remove the outliers in the classification map, \pkg{sits} uses \code{sits_smooth()}. Its main parameters are: (a) \code{cube}, a probability cube; (b) \code{window_size}, the dimension of the local neighbourhood; (c) \code{neigh_fraction}, the percentage of pixels in the neighbourhood used to calculate the variance; (d) \code{smoothness}, a vector with  prior logit variances for each class; (e) \code{output_dir}, directory where results will be stored; (f) \code{version}, a string to distinguish different runs.

As discussed above, the effect of the Bayesian estimator depends on the values of the a priori variance $\sigma^2_{k}$ set by the user and of the neighbourhood definition used to compute to local variance $s^2_{i,1}$ for each pixel. To show the effects of different $\sigma^2$ values we consider two cases: (a) setting $\sigma^2$ to a high value close to the maximum value of local logit variance; (b) setting $\sigma^2$ to a lower value close to the minimum value of the 4rd quartile. 

```{r, echo=TRUE, eval=TRUE}
smooth_cube_high <- sits_smooth(
    cube = probs_cube,
    window_size = 7,
    neigh_fraction = 0.5,
    smoothness = c(25, 10, 20, 20, 25, 10),
    output_dir = tempdir(),
    version = "smooth_high")
```

The impact of Bayesian smoothing can be best captured by producing  a labelled map using \code{sits_label_classification()} taking the smoothed image as its input. Figure \@ref(fig:smth1) shows that the outliers and isolated pixels have been removed.

```{r smth1, width = 7, tidy="styler", fig.align = 'center', fig.cap = "Labelled map with smoothing with high smoothness values."}
label_cube_smooth_high <- sits_label_classification(
    cube = smooth_cube_high,
    output_dir = tempdir(),
    version = "smooth_high")
plot(label_cube_smooth_high)
```

In the smoothed map, the outliers have been removed by expanding forest areas. Forests have replaced small corridors of water and soil encircled by trees. This effect is due to the high probability of forest detection in the training data. Compare the smoothing with high values with the smoothing with values close to the minimum value of the 4th quartile of the local variance for each class, as computed below.

```{r, echo=TRUE, eval=TRUE}
smooth_cube_low <- sits_smooth(
    cube = probs_cube,
    window_size = 7,
    neigh_fraction = 0.5,
    smoothness = c(5, 1, 1, 2, 4, 1),
    output_dir = tempdir(),
    version = "smooth_low")
```

To see the impact of small $\sigma^2$, we compute the labelled map.

```{r smth2, width = 9, tidy="styler", fig.align = 'center', fig.cap = "Labelled map with small smoothing parameters."}
label_cube_smooth_low <- sits_label_classification(
    cube = smooth_cube_low,
    output_dir = tempdir(),
    version = "smooth_low")
plot(label_cube_smooth_low)
```

Comparing the class areas of the non-smoothed and smoothed maps shown below, the most frequent classes (\code{ClearCut_Soil} and \code{Forest}) increased their areas at the expense of the others. As shown in Figure \@ref(fig:fig1), these classes occur in more compact patches than the others. 

```{r, echo=TRUE, eval=TRUE}
sum1 <- summary(label_cube_no_smooth, only_stats = TRUE)
names(sum1) <- c("class", "area_k2_no_smooth")
sum2 <- summary(label_cube_smooth_high, only_stats = TRUE)
names(sum2) <- c("class", "area_k2_smooth_high")
sum3 <- summary(label_cube_smooth_low, only_stats = TRUE)
names(sum3) <- c("class", "area_k2_smooth_low")
dplyr::inner_join(sum1, sum2, by = "class") %>% 
  dplyr::inner_join(sum3, by = "class")
```

In the smoothed map, the outliers have been removed by expanding forest areas. Forests have replaced small corridors of water and soil encircled by trees. This effect is due to the high probability of forest detection in the training data. To keep the water areas and reduce the expansion of the forest area, a viable alternative is to reduce the smoothness ($\sigma^2$) for the "Forest" and "Water" classes. In this way, the local influence of the forest in the other classes is reduced. As for the water areas, since they are narrow, their neighborhoods will have many low probability values, which would reduce the expected value of the Bayesian estimator. 

Based on expert knowledge, there are two main options for setting the $\sigma^2_{k}$ parameter:
    
1. To increase the neighbourhood influence compared with the probability values for each pixel, set the $\sigma^2_{k}$ parameter with high values (20 or above) . Classes whose probabilities have strong spatial autocorrelation will tend to replace outliers of classes with higher spatial variance variability.

2. To reduce the neighbourhood influence compared with the probabilities for each pixel of class $k$, set the $\sigma^2_{k}$ parameter with low values (5 or below) . In this way, classes with low spatial autocorrelation are more likely not to be relabelled.

Consider the case of forest areas and watersheds. If an expert wishes to have compact areas classified as forests without many outliers inside them, she will set the $\sigma^2$ parameter for the class "Forest" to be high. For comparison, to avoid that small watersheds with few similar neighbors being relabeled, it is advisable to avoid a strong influence of the neighbors, setting $\sigma^2$ to be as low as possible. Therefore, choice of $\sigma^2$ depends on the effect intended by the expert in the final clasified map. 

To keep the water areas and reduce the expansion of the forest area, a viable alternative is to reduce the smoothness ($\sigma^2$) for the "Forest" and "Water" classes. In this way, the local influence of the forest in the other classes is reduced. As for the water areas, since they are narrow, their neighborhoods will have many low probability values, which would reduce the expected value of the Bayesian estimator.

# Comparison with other methods 

# Conclusion
